### 2011-05-15 annualreports/2011/balancesheet.tex
Draft of the 2011 report.

\section{Balance Sheet}
31\superscript{st} March 2009

\begin{center}
\begin{tabular}{  l  r  r }
\toprule
                            & \multicolumn{2}{c}{2009} \\
\cmidrule(r){2-3}
                            & £     & £ \\
    \multicolumn{2}{c}{{\bf Fixed Assets}} &\\
    {\bf Tangible fixed assets}   &       & 1,054 \\ \cmidrule{2-3} \\
    \multicolumn{2}{c}{{\bf Current Assets}}&\\
    Cash at bank and in hand & 8,642 & \\
    Creditors: amounts falling due within one year & -1,343 & \\
    {\bf Net current assets}    &   & 7,299 \\ \cmidrule{2-3} \\
    {\bf Total assets less current liabilities} & & 8,354 \\ \cmidrule{2-3} \\
    \multicolumn{2}{c}{{\bf Capital and Reserves}}&\\
    Income and expenditure account     &   &   8,354 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on 6\superscript{th} September 2010.
\vspace{48pt}

>>>>

\section{Balance Sheet}
31\superscript{st} March 2011

\begin{center}
\begin{tabular}{  l  r  r r r}
\toprule
                            & \multicolumn{2}{c}{2011} &  \multicolumn{2}{c}{2010} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
                                                & £     & £     & £     & £     \\
{\bf Fixed Assets}                              &       &       &       &       \\
{\bf Tangible fixed assets}                     &       & 5,337 &       & 1,054 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Current Assets}                            &       &       &       &       \\
Rental Deposit                                  & 7,696 &       &       &       \\
Cash at bank and in hand                        & 7,568 &       & 8,642 &       \\
Creditors: amounts falling due within one year  & -1,979 &      & -1,343&      \\
{\bf Net current assets}                        &       & 13,285&       & 7,299 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Total assets less current liabilities}     &       & 18,622&       & 8,354 \\
\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
{\bf Capital and Reserves}&\\
Income and expenditure account                  &       & 10,269&       & 8,354 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on <date>
\vspace{48pt}
